Tweet Classification: Filtering \\ of Twitter for Company-relevant Tweets

### 2012-12-07 paper/paper.tex
paper

[INSERT LIST OF KEYWORDS]...\\
"apple", "itunes", "ipad", "ipod", "mac", "ios", "iphone", "AAPL", "cupertino", "safari", "ilife", "iwork", "garageband", "ibook", "powerbook", "itouch", "app store", "macworld", "facetime", "icloud", "mobileme", "siri", "imovie", "iphoto", "quicktime", "logic pro", "think different" \\

@@

This table of most common features for various pipelines shows the large effect that preprocessing steps like stopword removal, capitalization normalization, bigramming, and tokenization have on the feature distribution. It is interesting that `...' appears as a very common feature using our Twitter-aware tokenizer.

@@

\section{Team Contributions}
Specific team member contributions followed from what we originally stated when the project began. Brandon was in charge of writing some of the Java classes that would be used by the Mallet solftware to push and pull tweets to and from the server where they were stored. He also wrote and researched about different Pipes that could be used by Mallet to transform the tweets being classified. Finally, Brandon had a hand in defining the project structure, and helped edit the project's paper and website. Curtis, being the resident expert in the Mallet software, was tasked with integrating it into the project. He also wrote the majority of the paper and did extensive work, writing Pipes to manipulate tweet data. Dan initally set up a server to pull tweets from Twitter so we would have a large data set to work with. From there he hand built a testing suite to analyze the impact each of the Pipes had on classification. Because of this, Dan also compiled the majority of the statistical results that came from running his test suite.

We, Brandon Maxwell, Curtis Ullerich, and Daniel Stiner, hereby concur with the contents of this report, in the knowledge that it is an accurate representation of the work we did and the results we found, for our term project.

>>>>

\quote{\textit{apple, itunes, ipad, ipod, mac, ios, iphone, AAPL, cupertino, safari, ilife, iwork, garageband, ibook, powerbook, itouch, app store, macworld, facetime, icloud, mobileme, siri, imovie, iphoto, quicktime, logic pro, think different}} \\

@@

This table of most common features for various pipelines shows the large effect that preprocessing steps like stopword removal, capitalization normalization, bigramming, and tokenization have on the feature distribution. The bigrams iphone\_5 and my\_iphone prove to be useful when finding tweets about Apple and the bigrams new\_post and apple\_juice are useful when finding tweets not about Apple. Note the case of the word `apple' in its various forms. It appears most commonly as `Apple' in tweets about apple and lowercased in other tweets. This is expected, but there is also a high incidence of the word `Apple' in tweets not about the company. It is interesting that `...' appears as a very common feature using our Twitter-aware tokenizer, as well as the token `rt'. These appear with equal weight in tweets both about and not about Apple, so we may benefit from removal them during tokenization.\\

@@
